Estimation of flow trajectories in a multiple lines network

### 2022-04-25 presentation_bb/presentation_bb.tex
Presentation updated

\usepackage [autostyle, english = american]{csquotes}
\usepackage{bm}

@@

	\begin{frame}{The multiple lines network}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				Having only lines data, we have a \imp{disconnected oriented graph}. \linebreak

				In addition to \imp{line edges}, it is possible to construct \imp{transfer edges} to make the graph connected, by using, e.g.,
				\begin{itemize}
					\item Superstops names,
					\item Pedestrian time,
					\item Distance.
				\end{itemize} 
				\vspace{0.4cm}
				This is what we call a \imp{multiple lines network}.
			\end{column}
			\begin{column}{0.5\textwidth} 
				\begin{center}
					\includegraphics[width=0.8\textwidth]{img/stop_area_c.png} \\
					\vspace{0.5cm}
					\includegraphics[width=0.7\textwidth]{img/edge_type2.png}
				\end{center}
			\end{column}
		\end{columns}
	\end{frame}

@@

	\begin{frame}{Formal problem definition}
		Let a line (in one direction), which have $n$ stops. Let $\bm{\rho}_\text{in} = (\rho^\text{in}_i)$ and $\bm{\rho}_\text{out} = (\rho^\text{out}_i)$ be two vectors representing, respectively, the passengers entering and leaving the line at each stops.
	\end{frame}

>>>>

\usepackage [autostyle, english = american]{csquotes}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}

@@

	\begin{frame}{The multiple lines network}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				Having only lines data, the structure is a \imp{disconnected oriented graph}. \linebreak

				In addition to \imp{line edges}, it is possible to construct \imp{transfer edges} to make the graph connected, by using, e.g.,
				\begin{itemize}
					\item Superstops names,
					\item Pedestrian time,
					\item Distance.
				\end{itemize} 
				\vspace{0.4cm}
				With transfer edges, we have a \imp{unilaterally connected graph}.
			\end{column}
			\begin{column}{0.5\textwidth} 
				\begin{center}
					\includegraphics[width=0.8\textwidth]{img/stop_area_c.png} \\
					\vspace{0.5cm}
					\includegraphics[width=0.7\textwidth]{img/edge_type2.png}
				\end{center}
			\end{column}
		\end{columns}
	\end{frame}

@@

	\begin{frame}{Formal problem definition}
		Let a line (in one direction), which have $n$ stops. Let $\bm{\rho}_\text{in} = (\rho^\text{in}_s)$ and $\bm{\rho}_\text{out} = (\rho^\text{out}_t)$ be two vectors representing, respectively, the \imp{passengers entering and leaving lines at each stop}. \\
		\vspace{0.4cm}
		We search a $(n \times n)$ \imp{origin-destination matrix} $\mathbf{N} = (n_{st})$ where components represents
		$$
			n_{st} = \text{"\imp{the number of passengers entering line at $s$ and leaving at $t$}"}.
		$$
		These components must verify
		\begin{enumerate}
			\item $n_{st} \geq 0$,
			\item $n_{s\bullet} = \rho^\text{in}_s$,
			\item $n_{\bullet t} = \rho^\text{out}_t$.
		\end{enumerate}
		\small ($\bullet$ indicates a sum on the replaced index)
	\end{frame}

	\begin{frame}{Formal problem definition}
		$$
		 \mathbf{N} = \bordermatrix{
			   & \sigma^\text{out}_1 & \sigma^\text{out}_2  & \cdots & \sigma^\text{out}_{n-1} & \sigma^\text{out}_n   \cr
			\sigma^\text{in}_1 & n_{11} & n_{12} & \cdots & n_{1,n-1} & n_{1n} \cr
			\sigma^\text{in}_2 & n_{21} & n_{22} & \cdots & n_{2,n-1} & n_{2n} \cr
			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots \cr
			\sigma^\text{in}_{n-1} & n_{n-1,1} & n_{n-1,2} & \cdots & n_{n-1,n-1} & n_{n-1,n} \cr
			\sigma^\text{in}_{n} & n_{n,1} & n_{n,2} & \cdots & n_{n,n-1} & n_{n,n}}
		$$
	\end{frame}
